---
title: "dataCombining"
author: "Ross Nygard"
date: "`r Sys.Date()`"
output: html_document
---
> HEY ANYTHING I PUT IN LIKE THIS WILL PROB WANNA BE DELETED LATER JUST AN FYI

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Setting up the rain event data frame

This code chunk will serve to modify the rain event characteristic data frame to be more easily compared to the other data frames developed later.
```{r Rain Event}
# Rainfall/Runoff Characteristics
RF_RO_chara.df <- read_csv('Data/commaSeparatedValues/RF_RO_Event_Characteristics.csv',
                           col_types = cols(.default = col_character())) %>%
# Rename columns to include units
  rename("PHD [hr]" = "PHD",                  # Previous dry hours
         "d_rain [min]" = "d_rain",           # Duration of the rain event
         "h_rain [in]" = "h_rain",            # Depth of the rain event
         "i_rain-max [mm/hr]" = "i_rain-max", # Rainfall maximum intensity
         "IPRT [min]" = "IPRT",               # Initial pavement residence time
         "V_runoff [L]" = "V_runoff",         # Volume of runoff
         "C [-]" = "C",                       # Runoff coefficient
         "Q_inf-max [L/s]" = "Qinf-max",      # Maximum influent flow rate
         "Q_inf-avg [L/s]" = "Qinf-avg",      # Average influent flow rate
         "Q_eff-max [L/s]" = "Qeff-max",      # Maximum effluent flow rate
         "Q_eff-avg [L/s]" = "Qeff-avg",      # Average effluent flow rate
         "n_inf [-]" = "n_inf",               # Number of influent samples
         "n_eff [-]" = "n_eff") %>%            # Number of effluent samples
  slice(-1) %>%  # Remove the row containing units
  select(-Event) # Remove the event count column
```

## Setting up the rain characteristic data frame

This code chunk will serve to combine multiple files into one rain characteristic data frame.

```{r}
# Read in RainMeanCharacteristics1.csv
rain_chara_1.df <- read_csv("Data/commaSeparatedValues/RainMeanCharacteristics1.csv",
                            col_types = cols(.default = col_character())) %>% # Read in the file
  # Rename columns to include units
  rename("Date" = "Rainfall/Runoff event",   # Date for ease of joining later
         "Cl(-) [ug/L]" = "Cl(-)",           # Chloride concentration
         "SO4(2-) [ug/L]" = "SO4 (2-)",      # Sulfate concentration
         "PO4(3-) [ug/L]" = "PO4 (3-)",      # Phosphate concentration
         "NH3-N [ug/L]" = "NH3-N",           # Ammonia concentration
         "NO3(-)-N [ug/L]" = "NO3(-)-N",     # Nitrate concentration
         "TDN [ug/L]" = "TDN",               # Total dissolved nitrogen
         "COD [mg/L]" = "COD",               # Chemical oxygen demand
         "Turbidity [NTU]" = "Turbidity",    # Turbidity
         "NO2(-)-N [ug/L]" = "NO2(-)-N") %>% # Nitrite concentration
  slice(-1) # Remove the row containing units

# Read in RainMeanCharacteristics2.csv
rain_chara_2.df <- read_csv("Data/commaSeparatedValues/RainMeanCharacteristics2.csv",
                            col_types = cols(.default = col_character())) %>%  # Units were already included in top row, so full renaming is not necessary
  rename("Date" = `Rainfall/Runoff event`)

rain_chara_full.df <- full_join(rain_chara_1.df, rain_chara_2.df, by = "Date")
```


## Setting up influent data frame

This code chunk will serve to combine multiple data sets into one influent average characteristic dataframe.

> Would it be helpful to keep the max and mins for each characteristic in?

```{r}

```



